An investigation into using scagnostics to find interesting projections of high-dimensional data

### 2018-10-24 scagnostics.Rmd
Remark about spiral.

\textcolor{red}{\cite{posse95a} uses simulations with "strongly hidden structure", i.e. truncated Gaussian distributions with approximately identity covariance matrix, such that they don't appear in any of the principal component planes.}

>>>>

\textcolor{red}{\cite{posse95a} uses simulations with "strongly hidden structure", i.e. truncated Gaussian distributions with approximately identity covariance matrix, such that they don't appear in any of the principal component planes. In particular seems that spiral is hardest to identify based on results from Posse, maybe I can add this to my sphere dataset? or instead of it?}
